---
title: 'Population density affects sexual selection in an insect model'
author: "Lennart Winkler^1^, Ronja Eilhardt^1^ & Tim Janicke^1,2^ <br></br>  ^1^Applied Zoology, Technical University Dresden <br> ^2^Centre d’Écologie Fonctionnelle et Évolutive, UMR 5175, CNRS, Université de Montpellier</br>"
subtitle: 'Part 5: Total sexual selection on males'
site: workflowr::wflow_site
output:
  workflowr::wflow_html
---

Supplementary material reporting R code for the manuscript 'Population density affects sexual selection in an insect model'.

# Part 5: Total sexual selection on males

Finally, we calculated the total opportunity for sexual selection (ITS) for males as
I_TS=var(MS)+var(PS)+2 cov(MS,PS).
We used relativized data and bootstrapping to estimate ITS and two-sided permutation tests to compare it between treatments.

# Load and prepare data

Before we started the analyses, we loaded all necessary packages and data.

```{r Load, message=FALSE, warning=FALSE, results='hide'}
rm(list = ls()) # Clear work environment

# Load R-packages ####
list_of_packages=cbind('ggeffects','ggplot2','gridExtra','lme4','lmerTest','readr','dplyr','EnvStats','cowplot','gridGraphics','car','RColorBrewer','boot','data.table','base','ICC','knitr')
lapply(list_of_packages, require, character.only = TRUE) 

# Load data set ####
D_data=read_delim("./data/Data_Winkler_et_al_2023_Denstiy.csv",";", escape_double = FALSE, trim_ws = TRUE)

# Set factors and levels for factors
D_data$Week=as.factor(D_data$Week)
D_data$Sex=as.factor(D_data$Sex)
D_data$Gr_size=as.factor(D_data$Gr_size)
D_data$Gr_size <- factor(D_data$Gr_size, levels=c("SG","LG"))
D_data$Arena=as.factor(D_data$Arena)

## Subset data set ####
### Data according to denstiy ####
D_data_0.26=D_data[D_data$Treatment=='D = 0.26',]
D_data_0.52=D_data[D_data$Treatment=='D = 0.52',]
D_data_0.67=D_data[D_data$Treatment=='D = 0.67',]
D_data_1.33=D_data[D_data$Treatment=='D = 1.33',]

### Subset data by sex ####
D_data_m=D_data[D_data$Sex=='M',]
D_data_f=D_data[D_data$Sex=='F',]

### Calculate data relativized within treatment and sex ####
# Small group + large Area
D_data_0.26=D_data[D_data$Treatment=='D = 0.26',]

D_data_0.26$rel_m_RS=NA
D_data_0.26$rel_m_prop_RS=NA
D_data_0.26$rel_m_cMS=NA
D_data_0.26$rel_m_InSuc=NA
D_data_0.26$rel_m_feSuc=NA
D_data_0.26$rel_m_pFec=NA
D_data_0.26$rel_m_PS=NA
D_data_0.26$rel_m_pFec_compl=NA

D_data_0.26$rel_f_RS=NA
D_data_0.26$rel_f_prop_RS=NA
D_data_0.26$rel_f_cMS=NA
D_data_0.26$rel_f_fec_pMate=NA

D_data_0.26$rel_m_RS=D_data_0.26$m_RS/mean(D_data_0.26$m_RS,na.rm=T)
D_data_0.26$rel_m_prop_RS=D_data_0.26$m_prop_RS/mean(D_data_0.26$m_prop_RS,na.rm=T)
D_data_0.26$rel_m_cMS=D_data_0.26$m_cMS/mean(D_data_0.26$m_cMS,na.rm=T)
D_data_0.26$rel_m_InSuc=D_data_0.26$m_InSuc/mean(D_data_0.26$m_InSuc,na.rm=T)
D_data_0.26$rel_m_feSuc=D_data_0.26$m_feSuc/mean(D_data_0.26$m_feSuc,na.rm=T)
D_data_0.26$rel_m_pFec=D_data_0.26$m_pFec/mean(D_data_0.26$m_pFec,na.rm=T)
D_data_0.26$rel_m_PS=D_data_0.26$m_PS/mean(D_data_0.26$m_PS,na.rm=T)
D_data_0.26$rel_m_pFec_compl=D_data_0.26$m_pFec_compl/mean(D_data_0.26$m_pFec_compl,na.rm=T)

D_data_0.26$rel_f_RS=D_data_0.26$f_RS/mean(D_data_0.26$f_RS,na.rm=T)
D_data_0.26$rel_f_prop_RS=D_data_0.26$f_prop_RS/mean(D_data_0.26$f_prop_RS,na.rm=T)
D_data_0.26$rel_f_cMS=D_data_0.26$f_cMS/mean(D_data_0.26$f_cMS,na.rm=T)
D_data_0.26$rel_f_fec_pMate=D_data_0.26$f_fec_pMate/mean(D_data_0.26$f_fec_pMate,na.rm=T)

# Large group + large Area
D_data_0.52=D_data[D_data$Treatment=='D = 0.52',]
#Relativize data

D_data_0.52$rel_m_RS=NA
D_data_0.52$rel_m_prop_RS=NA
D_data_0.52$rel_m_cMS=NA
D_data_0.52$rel_m_InSuc=NA
D_data_0.52$rel_m_feSuc=NA
D_data_0.52$rel_m_pFec=NA
D_data_0.52$rel_m_PS=NA
D_data_0.52$rel_m_pFec_compl=NA

D_data_0.52$rel_f_RS=NA
D_data_0.52$rel_f_prop_RS=NA
D_data_0.52$rel_f_cMS=NA
D_data_0.52$rel_f_fec_pMate=NA

D_data_0.52$rel_m_RS=D_data_0.52$m_RS/mean(D_data_0.52$m_RS,na.rm=T)
D_data_0.52$rel_m_prop_RS=D_data_0.52$m_prop_RS/mean(D_data_0.52$m_prop_RS,na.rm=T)
D_data_0.52$rel_m_cMS=D_data_0.52$m_cMS/mean(D_data_0.52$m_cMS,na.rm=T)
D_data_0.52$rel_m_InSuc=D_data_0.52$m_InSuc/mean(D_data_0.52$m_InSuc,na.rm=T)
D_data_0.52$rel_m_feSuc=D_data_0.52$m_feSuc/mean(D_data_0.52$m_feSuc,na.rm=T)
D_data_0.52$rel_m_pFec=D_data_0.52$m_pFec/mean(D_data_0.52$m_pFec,na.rm=T)
D_data_0.52$rel_m_PS=D_data_0.52$m_PS/mean(D_data_0.52$m_PS,na.rm=T)
D_data_0.52$rel_m_pFec_compl=D_data_0.52$m_pFec_compl/mean(D_data_0.52$m_pFec_compl,na.rm=T)

D_data_0.52$rel_f_RS=D_data_0.52$f_RS/mean(D_data_0.52$f_RS,na.rm=T)
D_data_0.52$rel_f_prop_RS=D_data_0.52$f_prop_RS/mean(D_data_0.52$f_prop_RS,na.rm=T)
D_data_0.52$rel_f_cMS=D_data_0.52$f_cMS/mean(D_data_0.52$f_cMS,na.rm=T)
D_data_0.52$rel_f_fec_pMate=D_data_0.52$f_fec_pMate/mean(D_data_0.52$f_fec_pMate,na.rm=T)

# Small group + small Area
D_data_0.67=D_data[D_data$Treatment=='D = 0.67',]
#Relativize data
D_data_0.67$rel_m_RS=NA
D_data_0.67$rel_m_prop_RS=NA
D_data_0.67$rel_m_cMS=NA
D_data_0.67$rel_m_InSuc=NA
D_data_0.67$rel_m_feSuc=NA
D_data_0.67$rel_m_pFec=NA
D_data_0.67$rel_m_PS=NA
D_data_0.67$rel_m_pFec_compl=NA

D_data_0.67$rel_f_RS=NA
D_data_0.67$rel_f_prop_RS=NA
D_data_0.67$rel_f_cMS=NA
D_data_0.67$rel_f_fec_pMate=NA

D_data_0.67$rel_m_RS=D_data_0.67$m_RS/mean(D_data_0.67$m_RS,na.rm=T)
D_data_0.67$rel_m_prop_RS=D_data_0.67$m_prop_RS/mean(D_data_0.67$m_prop_RS,na.rm=T)
D_data_0.67$rel_m_cMS=D_data_0.67$m_cMS/mean(D_data_0.67$m_cMS,na.rm=T)
D_data_0.67$rel_m_InSuc=D_data_0.67$m_InSuc/mean(D_data_0.67$m_InSuc,na.rm=T)
D_data_0.67$rel_m_feSuc=D_data_0.67$m_feSuc/mean(D_data_0.67$m_feSuc,na.rm=T)
D_data_0.67$rel_m_pFec=D_data_0.67$m_pFec/mean(D_data_0.67$m_pFec,na.rm=T)
D_data_0.67$rel_m_PS=D_data_0.67$m_PS/mean(D_data_0.67$m_PS,na.rm=T)
D_data_0.67$rel_m_pFec_compl=D_data_0.67$m_pFec_compl/mean(D_data_0.67$m_pFec_compl,na.rm=T)

D_data_0.67$rel_f_RS=D_data_0.67$f_RS/mean(D_data_0.67$f_RS,na.rm=T)
D_data_0.67$rel_f_prop_RS=D_data_0.67$f_prop_RS/mean(D_data_0.67$f_prop_RS,na.rm=T)
D_data_0.67$rel_f_cMS=D_data_0.67$f_cMS/mean(D_data_0.67$f_cMS,na.rm=T)
D_data_0.67$rel_f_fec_pMate=D_data_0.67$f_fec_pMate/mean(D_data_0.67$f_fec_pMate,na.rm=T)

# Large group + small Area
D_data_1.33=D_data[D_data$Treatment=='D = 1.33',]
#Relativize data

D_data_1.33$rel_m_RS=NA
D_data_1.33$rel_m_prop_RS=NA
D_data_1.33$rel_m_cMS=NA
D_data_1.33$rel_m_InSuc=NA
D_data_1.33$rel_m_feSuc=NA
D_data_1.33$rel_m_pFec=NA
D_data_1.33$rel_m_PS=NA
D_data_1.33$rel_m_pFec_compl=NA

D_data_1.33$rel_f_RS=NA
D_data_1.33$rel_f_prop_RS=NA
D_data_1.33$rel_f_cMS=NA
D_data_1.33$rel_f_fec_pMate=NA

D_data_1.33$rel_m_RS=D_data_1.33$m_RS/mean(D_data_1.33$m_RS,na.rm=T)
D_data_1.33$rel_m_prop_RS=D_data_1.33$m_prop_RS/mean(D_data_1.33$m_prop_RS,na.rm=T)
D_data_1.33$rel_m_cMS=D_data_1.33$m_cMS/mean(D_data_1.33$m_cMS,na.rm=T)
D_data_1.33$rel_m_InSuc=D_data_1.33$m_InSuc/mean(D_data_1.33$m_InSuc,na.rm=T)
D_data_1.33$rel_m_feSuc=D_data_1.33$m_feSuc/mean(D_data_1.33$m_feSuc,na.rm=T)
D_data_1.33$rel_m_pFec=D_data_1.33$m_pFec/mean(D_data_1.33$m_pFec,na.rm=T)
D_data_1.33$rel_m_PS=D_data_1.33$m_PS/mean(D_data_1.33$m_PS,na.rm=T)
D_data_1.33$rel_m_pFec_compl=D_data_1.33$m_pFec_compl/mean(D_data_1.33$m_pFec_compl,na.rm=T)

D_data_1.33$rel_f_RS=D_data_1.33$f_RS/mean(D_data_1.33$f_RS,na.rm=T)
D_data_1.33$rel_f_prop_RS=D_data_1.33$f_prop_RS/mean(D_data_1.33$f_prop_RS,na.rm=T)
D_data_1.33$rel_f_cMS=D_data_1.33$f_cMS/mean(D_data_1.33$f_cMS,na.rm=T)
D_data_1.33$rel_f_fec_pMate=D_data_1.33$f_fec_pMate/mean(D_data_1.33$f_fec_pMate,na.rm=T)

### Reduce treatments to arena and population size ####
# Arena size
D_data_Large_arena=rbind(D_data_0.26,D_data_0.52)
D_data_Small_arena=rbind(D_data_0.67,D_data_1.33)

# Population size
D_data_Small_pop=rbind(D_data_0.26,D_data_0.67)
D_data_Large_pop=rbind(D_data_0.52,D_data_1.33)

## Set figure schemes ####
# Set color-sets for figures
colpal=brewer.pal(4, 'Dark2')
colpal2=c("#b2182b","#2166AC")
colpal3=brewer.pal(4, 'Paired')

# Set theme for ggplot2 figures
fig_theme=theme(panel.border = element_blank(),
                plot.margin = margin(0,2.2,0,0.2,"cm"),
                plot.title = element_text(hjust = 0.5),
                panel.background = element_blank(),
                legend.key=element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(), 
                legend.position = c(1.25, 0.8),
                plot.tag.position=c(0.01,0.98),
                legend.title = element_blank(),
                legend.text = element_text(colour="black", size=10),
                axis.line.x = element_line(colour = "black", size = 1),
                axis.line.y = element_line(colour = "black", size = 1),
                axis.text.x = element_text(face="plain", color="black", size=16, angle=0),
                axis.text.y = element_text(face="plain", color="black", size=16, angle=0),
                axis.title.x = element_text(size=16,face="plain", margin = margin(r=0,10,0,0)),
                axis.title.y = element_text(size=16,face="plain", margin = margin(r=10,0,0,0)),
                axis.ticks = element_line(size = 1),
                axis.ticks.length = unit(.3, "cm"))

## Create customized functions for analysis ####
# Create function to calculate standard error and upper/lower standard deviation
standard_error <- function(x) sd(x,na.rm=T) / sqrt(length(!is.na(x)))
upper_SD <- function(x) mean(x,na.rm=T)+(sd(x)/2)
lower_SD <- function(x) mean(x,na.rm=T)-(sd(x)/2)
```

We bootstrapped the total opportunity for sexual selection (ITS) for males.
```{r , warning=FALSE, message=FALSE, results='hide'}
## Bootstrapping total sexual selection on males ####

# Large arena size
D_data_Large_arena_M_totalSexSel <-as.data.table(cbind(D_data_Large_arena$rel_m_cMS,D_data_Large_arena$rel_m_PS))
c <- function(d, i){
  d2 <- d[i,]
  return(var(d2[,1], na.rm=TRUE)+var(d2[,2], na.rm=TRUE)+2*cov(d2[,1],d2[,2],use='pairwise.complete.obs'))
}
Large_arena_M__totalSexSel_bootvar <- boot(D_data_Large_arena_M_totalSexSel, c, R=10000)

# Small arena size
D_data_Small_arena_M_totalSexSel <-as.data.table(cbind(D_data_Small_arena$rel_m_cMS,D_data_Small_arena$rel_m_PS))

Small_arena_M__totalSexSel_bootvar <- boot(D_data_Small_arena_M_totalSexSel, c, R=10000)

# Large population size
D_data_Large_pop_M_totalSexSel <-as.data.table(cbind(D_data_Large_pop$rel_m_cMS,D_data_Large_pop$rel_m_PS))

Large_pop_M__totalSexSel_bootvar <- boot(D_data_Large_pop_M_totalSexSel, c, R=10000)

# Small population size
D_data_Small_pop_M_totalSexSel <-as.data.table(cbind(D_data_Small_pop$rel_m_cMS,D_data_Small_pop$rel_m_PS))

Small_pop_M__totalSexSel_bootvar <- boot(D_data_Small_pop_M_totalSexSel, c, R=10000)
rm(c)

### Extract data and write results table ####
PhenVarBoot_Table_Male_Large_arena_totalSexSel <- as.data.frame(cbind("Total sexual selection", "Large arena size", mean(Large_arena_M__totalSexSel_bootvar$t), quantile(Large_arena_M__totalSexSel_bootvar$t,.025, names = FALSE), quantile(Large_arena_M__totalSexSel_bootvar$t,.975, names = FALSE)))
PhenVarBoot_Table_Male_Small_arena_totalSexSel <- as.data.frame(cbind("Total sexual selection", "Small arena size", mean(Small_arena_M__totalSexSel_bootvar$t), quantile(Small_arena_M__totalSexSel_bootvar$t,.025, names = FALSE), quantile(Small_arena_M__totalSexSel_bootvar$t,.975, names = FALSE)))
PhenVarBoot_Table_Male_Large_pop_totalSexSel <- as.data.frame(cbind("Total sexual selection", "Large population size", mean(Large_pop_M__totalSexSel_bootvar$t), quantile(Large_pop_M__totalSexSel_bootvar$t,.025, names = FALSE), quantile(Large_pop_M__totalSexSel_bootvar$t,.975, names = FALSE)))
PhenVarBoot_Table_Male_Small_pop_totalSexSel <- as.data.frame(cbind("Total sexual selection", "Small population size", mean(Small_pop_M__totalSexSel_bootvar$t), quantile(Small_pop_M__totalSexSel_bootvar$t,.025, names = FALSE), quantile(Small_pop_M__totalSexSel_bootvar$t,.975, names = FALSE)))


totalSexSel_Table <- as.data.frame(as.matrix(rbind(PhenVarBoot_Table_Male_Large_arena_totalSexSel,PhenVarBoot_Table_Male_Small_arena_totalSexSel,
                                                   PhenVarBoot_Table_Male_Large_pop_totalSexSel,PhenVarBoot_Table_Male_Small_pop_totalSexSel)))

is.table(totalSexSel_Table)
colnames(totalSexSel_Table)[1] <- "Variance_component"
colnames(totalSexSel_Table)[2] <- "Treatment"
colnames(totalSexSel_Table)[3] <- "Variance"
colnames(totalSexSel_Table)[4] <- "l95_CI"
colnames(totalSexSel_Table)[5] <- "u95_CI"
totalSexSel_Table[,3]=round(as.numeric(totalSexSel_Table[,3]),digits=2)
totalSexSel_Table[,4]=round(as.numeric(totalSexSel_Table[,4]),digits=2)
totalSexSel_Table[,5]=round(as.numeric(totalSexSel_Table[,5]),digits=2)
rownames(totalSexSel_Table) <- c()
```

Table A7: Total opportunity for sexual selection (ITS) for males including 95% confidence intervals.
```{r , warning=FALSE, message=FALSE, layout="l-body-outset"}
kable(totalSexSel_Table)
```

## Permutation test for treatment comparisons

Next, we used permutation tests to compare the total opportunity for sexual selection between the treatments.
```{r , warning=FALSE, message=FALSE, results='hide'}
## Permutation test for treatment comparisons ####

# Arena size
Treat_diff_Male_arena_totalSexSel=cbind(Small_arena_M__totalSexSel_bootvar$t)-cbind(Large_arena_M__totalSexSel_bootvar$t)

t_Treat_diff_Male_arena_totalSexSel=mean(Treat_diff_Male_arena_totalSexSel,na.rm=TRUE)
t_Treat_diff_Male_arena_totalSexSel_lower=quantile(Treat_diff_Male_arena_totalSexSel,.025,na.rm=TRUE)
t_Treat_diff_Male_arena_totalSexSel_upper=quantile(Treat_diff_Male_arena_totalSexSel,.975,na.rm=TRUE)

# Permutation test to calculate p value
comb_data_MS=c(D_data_Large_arena$rel_m_cMS,D_data_Small_arena$rel_m_cMS)
comb_data_PS=c(D_data_Large_arena$rel_m_PS,D_data_Small_arena$rel_m_PS)

diff.observed = (var(na.omit((D_data_Small_arena$rel_m_cMS)))-var(na.omit((D_data_Large_arena$rel_m_cMS))))+ 
  (var(na.omit((D_data_Small_arena$rel_m_PS)))-var(na.omit((D_data_Large_arena$rel_m_PS))))+
  2*cov(((D_data_Small_arena$rel_m_cMS)),((D_data_Small_arena$rel_m_PS)), use = 'pairwise.complete.obs')-2*cov(((D_data_Large_arena$rel_m_cMS)),((D_data_Large_arena$rel_m_PS)), use = 'pairwise.complete.obs')


number_of_permutations = 100000
diff.random = NULL
for (i in 1 : number_of_permutations) {
  
  # Sample from the combined dataset
  a.random = sample (na.omit(comb_data_MS), length(c(D_data_Large_arena$rel_m_cMS)), TRUE)
  b.random = sample (na.omit(comb_data_MS), length(c(D_data_Small_arena$rel_m_cMS)), TRUE)
  c.random = sample (na.omit(comb_data_PS), length(c(D_data_Large_arena$rel_m_PS)), TRUE)
  d.random = sample (na.omit(comb_data_PS), length(c(D_data_Small_arena$rel_m_PS)), TRUE) 
  
  # Null (permuated) difference
  diff.random[i] = (var(na.omit((b.random)))-var(na.omit((a.random))))+ 
    (var(na.omit((d.random)))-var(na.omit((c.random))))+
    2*cov(((b.random)),((d.random)), use = 'pairwise.complete.obs')-2*cov(((a.random)),((c.random)), use = 'pairwise.complete.obs')
  
}

# P-value is the fraction of how many times the permuted difference is equal or more extreme than the observed difference

t_Treat_diff_Male_arena_totalSexSel_p = sum(abs(diff.random) >= as.numeric(abs(diff.observed)))/   number_of_permutations

# Group size
Treat_diff_Male_pop_totalSexSel=cbind(Large_pop_M__totalSexSel_bootvar$t)-cbind(Small_pop_M__totalSexSel_bootvar$t)

t_Treat_diff_Male_pop_totalSexSel=mean(Treat_diff_Male_pop_totalSexSel,na.rm=TRUE)
t_Treat_diff_Male_pop_totalSexSel_lower=quantile(Treat_diff_Male_pop_totalSexSel,.025,na.rm=TRUE)
t_Treat_diff_Male_pop_totalSexSel_upper=quantile(Treat_diff_Male_pop_totalSexSel,.975,na.rm=TRUE)

# Permutation test to calculate p value
comb_data_MS=c(D_data_Large_pop$rel_m_cMS,D_data_Small_pop$rel_m_cMS)
comb_data_PS=c(D_data_Large_pop$rel_m_InSuc,D_data_Small_pop$rel_m_PS)

diff.observed = (var(na.omit((D_data_Large_pop$rel_m_cMS)))-var(na.omit((D_data_Small_pop$rel_m_cMS))))+ 
  (var(na.omit((D_data_Large_pop$rel_m_PS)))-var(na.omit((D_data_Small_pop$rel_m_PS))))+
  2*cov(((D_data_Large_pop$rel_m_cMS)),((D_data_Large_pop$rel_m_PS)), use = 'pairwise.complete.obs')-2*cov(((D_data_Small_pop$rel_m_cMS)),((D_data_Small_pop$rel_m_PS)), use = 'pairwise.complete.obs')

number_of_permutations = 100000
diff.random = NULL
for (i in 1 : number_of_permutations) {
  
  # Sample from the combined dataset
  a.random = sample (na.omit(comb_data_MS), length(c(D_data_Large_pop$rel_m_cMS)), TRUE)
  b.random = sample (na.omit(comb_data_MS), length(c(D_data_Small_pop$rel_m_cMS)), TRUE)
  c.random = sample (na.omit(comb_data_PS), length(c(D_data_Large_pop$rel_m_PS)), TRUE)
  d.random = sample (na.omit(comb_data_PS), length(c(D_data_Small_pop$rel_m_PS)), TRUE) 
  
  # Null (permuated) difference
  diff.random[i] =  var(na.omit(a.random))-var(na.omit(b.random))
  
  diff.random[i] = (var(na.omit((a.random)))-var(na.omit((b.random))))+ 
    (var(na.omit((c.random)))-var(na.omit((d.random))))+
    2*cov(((a.random)),((c.random)), use = 'pairwise.complete.obs')-2*cov(((b.random)),((d.random)), use = 'pairwise.complete.obs')
  
}

# P-value is the fraction of how many times the permuted difference is equal or more extreme than the observed difference

t_Treat_diff_Male_pop_totalSexSel_p = sum(abs(diff.random) >= as.numeric(abs(diff.observed)))/   number_of_permutations

### Extract data and write results table ####
CompTreat_Table_Male_arena_totalSexSel <- as.data.frame(cbind("Arena size", "Total sexual selection", t_Treat_diff_Male_arena_totalSexSel, t_Treat_diff_Male_arena_totalSexSel_lower, t_Treat_diff_Male_arena_totalSexSel_upper, t_Treat_diff_Male_arena_totalSexSel_p))
names(CompTreat_Table_Male_arena_totalSexSel)=c('V1','V2','V3','V4','V5','V6')
CompTreat_Table_Male_pop_totalSexSel <- as.data.frame(cbind("Group size", "Total sexual selection", t_Treat_diff_Male_pop_totalSexSel, t_Treat_diff_Male_pop_totalSexSel_lower, t_Treat_diff_Male_pop_totalSexSel_upper, t_Treat_diff_Male_pop_totalSexSel_p))
names(CompTreat_Table_Male_pop_totalSexSel)=c('V1','V2','V3','V4','V5','V6')

Table_totalSexSel_TreatComp <- as.data.frame(as.matrix(rbind(CompTreat_Table_Male_arena_totalSexSel,CompTreat_Table_Male_pop_totalSexSel)))

colnames(Table_totalSexSel_TreatComp)[1] <- "Treatment"
colnames(Table_totalSexSel_TreatComp)[2] <- "Variance_component"
colnames(Table_totalSexSel_TreatComp)[3] <- "Variance"
colnames(Table_totalSexSel_TreatComp)[4] <- "l95_CI"
colnames(Table_totalSexSel_TreatComp)[5] <- "u95_CI"
colnames(Table_totalSexSel_TreatComp)[6] <- "p-value"
Table_totalSexSel_TreatComp[,3]=round(as.numeric(Table_totalSexSel_TreatComp[,3]),digits=2)
Table_totalSexSel_TreatComp[,4]=round(as.numeric(Table_totalSexSel_TreatComp[,4]),digits=2)
Table_totalSexSel_TreatComp[,5]=round(as.numeric(Table_totalSexSel_TreatComp[,5]),digits=2)
Table_totalSexSel_TreatComp[,6]=round(as.numeric(Table_totalSexSel_TreatComp[,6]),digits=3)
rownames(Table_totalSexSel_TreatComp) <- c()
```

Table A8: Treatment difference in the total opportunity for sexual selection (ITS) for males including 95% confidence intervals. Negative effect sizes indicate larger values at lower density and positive effect sizes larger values at higher density.
```{r , warning=FALSE, message=FALSE, layout="l-body-outset"}
kable(totalSexSel_Table)
```

## Plot: total sexual selection on males (Figure S9)

Finally, we plotted the total opportunity for sexual selection for each treatment.
```{r , warning=FALSE, message=FALSE, fig.align="left",fig.width = 5,fig.height=5, results='hide',fig.cap='Figure S9: Total opportunity for sexual selection (ITS) in males for group and arena size treatment. Mean and 95%CI estimated via bootstrapping. Dashed lines mark equal effect size for both densities. In grey area metrics were larger under high density treatments. The x-/y-distance of means from dashed line is equal to the effect size of the treatment.',fig.fullwidth=TRUE}
### Plot: total sexual selection on males (Figure S9) ####
# Reorder data
plot_totalSexSel_data_1=totalSexSel_Table[c(1,4),]
names(plot_totalSexSel_data_1)[3] <- "Variance_low"
names(plot_totalSexSel_data_1)[4] <- "lCI_low"
names(plot_totalSexSel_data_1)[5] <- "uCI_low"
plot_totalSexSel_data_2=totalSexSel_Table[c(2,3),c(3,4,5)]
names(plot_totalSexSel_data_2)[1] <- "Variance_high"
names(plot_totalSexSel_data_2)[2] <- "lCI_high"
names(plot_totalSexSel_data_2)[3] <- "uCI_high"
plot_totalSexSel_data=cbind(plot_totalSexSel_data_1,plot_totalSexSel_data_2)
plot_totalSexSel_data[c(2),2]='Group size'
plot_totalSexSel_data[c(1),2]='Arena size'

ggplot(plot_totalSexSel_data, aes(x=Variance_low, y=Variance_high, shape=Treatment)) + geom_abline(intercept = 0, slope = 1,size=1,linetype=2) +
  annotate(geom = "polygon", x = c(Inf, -Inf, -Inf), y = c(Inf, -Inf, Inf), fill = "grey", alpha = 0.2 )+
  geom_point(alpha=1,size = 5,color=colpal2[2])+
  geom_errorbar(alpha=0.5,size=1.1,width=0,color=colpal2[2], orientation='y',aes(xmin=lCI_low, xmax=uCI_low)) +geom_errorbar(alpha=0.5,size=1.1,color=colpal2[2],width=0, orientation='x', aes(ymin=lCI_high, ymax=uCI_high))+
  ylab(expression(paste('High density total ',~italic("I"['TS']))))+labs(tag = "")+xlab(expression(paste('Low density total ',~italic("I"['TS']))))+
  scale_shape_manual(values=c(15, 19))+
  guides(shape = guide_legend(override.aes = list(size = 3.5)))+
  xlim(0.1,0.7)+ylim(0.1,0.7)+
  guides(shape = guide_legend(override.aes = list(size = 5)))+
  fig_theme+theme(legend.position = c(1, 0.7))
```
