---
title: 'Population density affects sexual selection in an insect model'
author: "Lennart Winkler^1^, Ronja Eilhardt^1^ & Tim Janicke^1,2^ <br></br>  ^1^Applied Zoology, Technical University Dresden <br> ^2^Centre d’Écologie Fonctionnelle et Évolutive, UMR 5175, CNRS, Université de Montpellier</br>"
subtitle: 'Part 1: Analyses on the effect of the treatment on contact rates'
site: workflowr::wflow_site
output:
  workflowr::wflow_html
---

Supplementary material reporting R code for the manuscript 'Population density affects sexual selection in an insect model'.

# Part 1: Analyses on the effect of the treatment on contact rates

First, we tested for an effect of group and arena size on the number of contacts with potential mating partners.

# Load and prepare data

Before we started the analyses, we loaded all necessary packages and data.
```{r Load, message=FALSE, warning=FALSE, results='hide'}
rm(list = ls()) # Clear work environment

# Load R-packages ####
list_of_packages=cbind('ggeffects','ggplot2','gridExtra','lme4','lmerTest','readr','dplyr','EnvStats','cowplot','gridGraphics','car','RColorBrewer','boot','data.table','base','ICC','knitr')
lapply(list_of_packages, require, character.only = TRUE) 

# Load data set ####
D_data=read_delim("./data/Data_Winkler_et_al_2023_Denstiy.csv",";", escape_double = FALSE, trim_ws = TRUE)

# Set factors and levels for factors
D_data$Week=as.factor(D_data$Week)
D_data$Sex=as.factor(D_data$Sex)
D_data$Gr_size=as.factor(D_data$Gr_size)
D_data$Gr_size <- factor(D_data$Gr_size, levels=c("SG","LG"))
D_data$Arena=as.factor(D_data$Arena)

## Subset data set ####
### Data according to denstiy ####
D_data_0.26=D_data[D_data$Treatment=='D = 0.26',]
D_data_0.52=D_data[D_data$Treatment=='D = 0.52',]
D_data_0.67=D_data[D_data$Treatment=='D = 0.67',]
D_data_1.33=D_data[D_data$Treatment=='D = 1.33',]

### Subset data by sex ####
D_data_m=D_data[D_data$Sex=='M',]
D_data_f=D_data[D_data$Sex=='F',]

### Calculate data relativized within treatment and sex ####
# Small group + large Area
D_data_0.26=D_data[D_data$Treatment=='D = 0.26',]

D_data_0.26$rel_m_RS=NA
D_data_0.26$rel_m_prop_RS=NA
D_data_0.26$rel_m_cMS=NA
D_data_0.26$rel_m_InSuc=NA
D_data_0.26$rel_m_feSuc=NA
D_data_0.26$rel_m_pFec=NA
D_data_0.26$rel_m_PS=NA
D_data_0.26$rel_m_pFec_compl=NA

D_data_0.26$rel_f_RS=NA
D_data_0.26$rel_f_prop_RS=NA
D_data_0.26$rel_f_cMS=NA
D_data_0.26$rel_f_fec_pMate=NA

D_data_0.26$rel_m_RS=D_data_0.26$m_RS/mean(D_data_0.26$m_RS,na.rm=T)
D_data_0.26$rel_m_prop_RS=D_data_0.26$m_prop_RS/mean(D_data_0.26$m_prop_RS,na.rm=T)
D_data_0.26$rel_m_cMS=D_data_0.26$m_cMS/mean(D_data_0.26$m_cMS,na.rm=T)
D_data_0.26$rel_m_InSuc=D_data_0.26$m_InSuc/mean(D_data_0.26$m_InSuc,na.rm=T)
D_data_0.26$rel_m_feSuc=D_data_0.26$m_feSuc/mean(D_data_0.26$m_feSuc,na.rm=T)
D_data_0.26$rel_m_pFec=D_data_0.26$m_pFec/mean(D_data_0.26$m_pFec,na.rm=T)
D_data_0.26$rel_m_PS=D_data_0.26$m_PS/mean(D_data_0.26$m_PS,na.rm=T)
D_data_0.26$rel_m_pFec_compl=D_data_0.26$m_pFec_compl/mean(D_data_0.26$m_pFec_compl,na.rm=T)

D_data_0.26$rel_f_RS=D_data_0.26$f_RS/mean(D_data_0.26$f_RS,na.rm=T)
D_data_0.26$rel_f_prop_RS=D_data_0.26$f_prop_RS/mean(D_data_0.26$f_prop_RS,na.rm=T)
D_data_0.26$rel_f_cMS=D_data_0.26$f_cMS/mean(D_data_0.26$f_cMS,na.rm=T)
D_data_0.26$rel_f_fec_pMate=D_data_0.26$f_fec_pMate/mean(D_data_0.26$f_fec_pMate,na.rm=T)

# Large group + large Area
D_data_0.52=D_data[D_data$Treatment=='D = 0.52',]
#Relativize data

D_data_0.52$rel_m_RS=NA
D_data_0.52$rel_m_prop_RS=NA
D_data_0.52$rel_m_cMS=NA
D_data_0.52$rel_m_InSuc=NA
D_data_0.52$rel_m_feSuc=NA
D_data_0.52$rel_m_pFec=NA
D_data_0.52$rel_m_PS=NA
D_data_0.52$rel_m_pFec_compl=NA

D_data_0.52$rel_f_RS=NA
D_data_0.52$rel_f_prop_RS=NA
D_data_0.52$rel_f_cMS=NA
D_data_0.52$rel_f_fec_pMate=NA

D_data_0.52$rel_m_RS=D_data_0.52$m_RS/mean(D_data_0.52$m_RS,na.rm=T)
D_data_0.52$rel_m_prop_RS=D_data_0.52$m_prop_RS/mean(D_data_0.52$m_prop_RS,na.rm=T)
D_data_0.52$rel_m_cMS=D_data_0.52$m_cMS/mean(D_data_0.52$m_cMS,na.rm=T)
D_data_0.52$rel_m_InSuc=D_data_0.52$m_InSuc/mean(D_data_0.52$m_InSuc,na.rm=T)
D_data_0.52$rel_m_feSuc=D_data_0.52$m_feSuc/mean(D_data_0.52$m_feSuc,na.rm=T)
D_data_0.52$rel_m_pFec=D_data_0.52$m_pFec/mean(D_data_0.52$m_pFec,na.rm=T)
D_data_0.52$rel_m_PS=D_data_0.52$m_PS/mean(D_data_0.52$m_PS,na.rm=T)
D_data_0.52$rel_m_pFec_compl=D_data_0.52$m_pFec_compl/mean(D_data_0.52$m_pFec_compl,na.rm=T)

D_data_0.52$rel_f_RS=D_data_0.52$f_RS/mean(D_data_0.52$f_RS,na.rm=T)
D_data_0.52$rel_f_prop_RS=D_data_0.52$f_prop_RS/mean(D_data_0.52$f_prop_RS,na.rm=T)
D_data_0.52$rel_f_cMS=D_data_0.52$f_cMS/mean(D_data_0.52$f_cMS,na.rm=T)
D_data_0.52$rel_f_fec_pMate=D_data_0.52$f_fec_pMate/mean(D_data_0.52$f_fec_pMate,na.rm=T)

# Small group + small Area
D_data_0.67=D_data[D_data$Treatment=='D = 0.67',]
#Relativize data
D_data_0.67$rel_m_RS=NA
D_data_0.67$rel_m_prop_RS=NA
D_data_0.67$rel_m_cMS=NA
D_data_0.67$rel_m_InSuc=NA
D_data_0.67$rel_m_feSuc=NA
D_data_0.67$rel_m_pFec=NA
D_data_0.67$rel_m_PS=NA
D_data_0.67$rel_m_pFec_compl=NA

D_data_0.67$rel_f_RS=NA
D_data_0.67$rel_f_prop_RS=NA
D_data_0.67$rel_f_cMS=NA
D_data_0.67$rel_f_fec_pMate=NA

D_data_0.67$rel_m_RS=D_data_0.67$m_RS/mean(D_data_0.67$m_RS,na.rm=T)
D_data_0.67$rel_m_prop_RS=D_data_0.67$m_prop_RS/mean(D_data_0.67$m_prop_RS,na.rm=T)
D_data_0.67$rel_m_cMS=D_data_0.67$m_cMS/mean(D_data_0.67$m_cMS,na.rm=T)
D_data_0.67$rel_m_InSuc=D_data_0.67$m_InSuc/mean(D_data_0.67$m_InSuc,na.rm=T)
D_data_0.67$rel_m_feSuc=D_data_0.67$m_feSuc/mean(D_data_0.67$m_feSuc,na.rm=T)
D_data_0.67$rel_m_pFec=D_data_0.67$m_pFec/mean(D_data_0.67$m_pFec,na.rm=T)
D_data_0.67$rel_m_PS=D_data_0.67$m_PS/mean(D_data_0.67$m_PS,na.rm=T)
D_data_0.67$rel_m_pFec_compl=D_data_0.67$m_pFec_compl/mean(D_data_0.67$m_pFec_compl,na.rm=T)

D_data_0.67$rel_f_RS=D_data_0.67$f_RS/mean(D_data_0.67$f_RS,na.rm=T)
D_data_0.67$rel_f_prop_RS=D_data_0.67$f_prop_RS/mean(D_data_0.67$f_prop_RS,na.rm=T)
D_data_0.67$rel_f_cMS=D_data_0.67$f_cMS/mean(D_data_0.67$f_cMS,na.rm=T)
D_data_0.67$rel_f_fec_pMate=D_data_0.67$f_fec_pMate/mean(D_data_0.67$f_fec_pMate,na.rm=T)

# Large group + small Area
D_data_1.33=D_data[D_data$Treatment=='D = 1.33',]
#Relativize data

D_data_1.33$rel_m_RS=NA
D_data_1.33$rel_m_prop_RS=NA
D_data_1.33$rel_m_cMS=NA
D_data_1.33$rel_m_InSuc=NA
D_data_1.33$rel_m_feSuc=NA
D_data_1.33$rel_m_pFec=NA
D_data_1.33$rel_m_PS=NA
D_data_1.33$rel_m_pFec_compl=NA

D_data_1.33$rel_f_RS=NA
D_data_1.33$rel_f_prop_RS=NA
D_data_1.33$rel_f_cMS=NA
D_data_1.33$rel_f_fec_pMate=NA

D_data_1.33$rel_m_RS=D_data_1.33$m_RS/mean(D_data_1.33$m_RS,na.rm=T)
D_data_1.33$rel_m_prop_RS=D_data_1.33$m_prop_RS/mean(D_data_1.33$m_prop_RS,na.rm=T)
D_data_1.33$rel_m_cMS=D_data_1.33$m_cMS/mean(D_data_1.33$m_cMS,na.rm=T)
D_data_1.33$rel_m_InSuc=D_data_1.33$m_InSuc/mean(D_data_1.33$m_InSuc,na.rm=T)
D_data_1.33$rel_m_feSuc=D_data_1.33$m_feSuc/mean(D_data_1.33$m_feSuc,na.rm=T)
D_data_1.33$rel_m_pFec=D_data_1.33$m_pFec/mean(D_data_1.33$m_pFec,na.rm=T)
D_data_1.33$rel_m_PS=D_data_1.33$m_PS/mean(D_data_1.33$m_PS,na.rm=T)
D_data_1.33$rel_m_pFec_compl=D_data_1.33$m_pFec_compl/mean(D_data_1.33$m_pFec_compl,na.rm=T)

D_data_1.33$rel_f_RS=D_data_1.33$f_RS/mean(D_data_1.33$f_RS,na.rm=T)
D_data_1.33$rel_f_prop_RS=D_data_1.33$f_prop_RS/mean(D_data_1.33$f_prop_RS,na.rm=T)
D_data_1.33$rel_f_cMS=D_data_1.33$f_cMS/mean(D_data_1.33$f_cMS,na.rm=T)
D_data_1.33$rel_f_fec_pMate=D_data_1.33$f_fec_pMate/mean(D_data_1.33$f_fec_pMate,na.rm=T)

### Reduce treatments to arena and population size ####
# Arena size
D_data_Large_arena=rbind(D_data_0.26,D_data_0.52)
D_data_Small_arena=rbind(D_data_0.67,D_data_1.33)

# Population size
D_data_Small_pop=rbind(D_data_0.26,D_data_0.67)
D_data_Large_pop=rbind(D_data_0.52,D_data_1.33)

## Set figure schemes ####
# Set color-sets for figures
colpal=brewer.pal(4, 'Dark2')
colpal2=c("#b2182b","#2166AC")
colpal3=brewer.pal(4, 'Paired')

# Set theme for ggplot2 figures
fig_theme=theme(panel.border = element_blank(),
                plot.margin = margin(0,2.2,0,0.2,"cm"),
                plot.title = element_text(hjust = 0.5),
                panel.background = element_blank(),
                legend.key=element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(), 
                legend.position = c(1.25, 0.8),
                plot.tag.position=c(0.01,0.98),
                legend.title = element_blank(),
                legend.text = element_text(colour="black", size=10),
                axis.line.x = element_line(colour = "black", size = 1),
                axis.line.y = element_line(colour = "black", size = 1),
                axis.text.x = element_text(face="plain", color="black", size=16, angle=0),
                axis.text.y = element_text(face="plain", color="black", size=16, angle=0),
                axis.title.x = element_text(size=16,face="plain", margin = margin(r=0,10,0,0)),
                axis.title.y = element_text(size=16,face="plain", margin = margin(r=10,0,0,0)),
                axis.ticks = element_line(size = 1),
                axis.ticks.length = unit(.3, "cm"))

## Create customized functions for analysis ####
# Create function to calculate standard error and upper/lower standard deviation
standard_error <- function(x) sd(x,na.rm=T) / sqrt(length(na.exclude(x)))
upper_CI <- function(x) mean(x,na.rm=T)+((standard_error(x))*qnorm(0.975))
lower_CI <- function(x) mean(x,na.rm=T)-((standard_error(x))*qnorm(0.975))

upper_SD <- function(x) mean(x,na.rm=T)+(sd(x)/2)
lower_SD <- function(x) mean(x,na.rm=T)-(sd(x)/2)
```

# Effect of density on contact rates of males

First, we calculated means and SE for all treatments:</br></br>
Mean number of contacts in small groups (SE) = `r round(mean(D_data_m$N_contact_WT[D_data_m$Gr_size=='SG'],na.rm=T),digits=2)` (`r round(standard_error(D_data_m$N_contact_WT[D_data_m$Gr_size=='SG']),digits=2)`)
```{r Mean number of contacts in small groups, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_m$N_contact_WT[D_data_m$Gr_size=='SG'],na.rm=T)
standard_error(D_data_m$N_contact_WT[D_data_m$Gr_size=='SG'])
```

Mean number of contacts in large groups (SE) = `r round(mean(D_data_m$N_contact_WT[D_data_m$Gr_size=='LG'],na.rm=T),digits=2)` (`r round(standard_error(D_data_m$N_contact_WT[D_data_m$Gr_size=='LG']),digits=2)`)
```{r Mean number of contacts in large groups, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_m$N_contact_WT[D_data_m$Gr_size=='LG'],na.rm=T)
standard_error(D_data_m$N_contact_WT[D_data_m$Gr_size=='LG'])
```

Mean number of contacts in large arena size (SE) = `r round(mean(D_data_m$N_contact_WT[D_data_m$Arena=='Large'],na.rm=T),digits=2)` (`r round(standard_error(D_data_m$N_contact_WT[D_data_m$Arena=='Large']),digits=2)`)
```{r Mean number of contacts in large arena size, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_m$N_contact_WT[D_data_m$Arena=='Large'],na.rm=T)
standard_error(D_data_m$N_contact_WT[D_data_m$Arena=='Large'])
```

Mean number of contacts in small arena size (SE) = `r round(mean(D_data_m$N_contact_WT[D_data_m$Arena=='Small'],na.rm=T),digits=2)` (`r round(standard_error(D_data_m$N_contact_WT[D_data_m$Arena=='Small']),digits=2)`)
```{r Mean number of contacts in small arena size, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_m$N_contact_WT[D_data_m$Arena=='Small'],na.rm=T)
standard_error(D_data_m$N_contact_WT[D_data_m$Arena=='Small'])
```

GLM for the effect of treatment on the number of contacts with potential partners:
```{r Model density effect on contact rates in males, warning=FALSE, message=FALSE}
mod1=glm((as.numeric(N_contact_WT))~Gr_size*Arena,data=D_data_m,family = quasipoisson) # GLM for treatment effect on contact rates of males
summary(mod1)
Anova(mod1,type=2) # Compute p-values via type 2 ANOVA
```
FDR corrected p-values:
```{r FDR corrected p-values, warning=FALSE, message=FALSE}
tab1=as.data.frame(round(p.adjust(c(0.0021530,0.0004615,0.2541364), method = 'fdr'),digits=3),row.names=cbind('Group size','Arena size', 'Interaction'))
colnames(tab1)<-cbind('P-value')
tab1
```

## Effect of density on contact rates of females

We calculated means and SE for all treatments:</br></br>
Mean number of contacts in small groups (SE) = `r round(mean(D_data_f$N_contact_WT[D_data_f$Gr_size=='SG'],na.rm=T),digits=2)` (`r round(standard_error(D_data_f$N_contact_WT[D_data_f$Gr_size=='SG']),digits=2)`)
```{r Mean number of contacts in small groups in females, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_f$N_contact_WT[D_data_f$Gr_size=='SG'],na.rm=T)
standard_error(D_data_f$N_contact_WT[D_data_f$Gr_size=='SG'])
```

Mean number of contacts in large groups (SE) = `r round(mean(D_data_f$N_contact_WT[D_data_f$Gr_size=='LG'],na.rm=T),digits=2)` (`r round(standard_error(D_data_f$N_contact_WT[D_data_f$Gr_size=='LG']),digits=2)`)
```{r Mean number of contacts in large groups in females, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_f$N_contact_WT[D_data_f$Gr_size=='LG'],na.rm=T)
standard_error(D_data_f$N_contact_WT[D_data_f$Gr_size=='LG'])
```

Mean number of contacts in large arena size (SE) = `r round(mean(D_data_f$N_contact_WT[D_data_f$Arena=='Large'],na.rm=T),digits=2)` (`r round(standard_error(D_data_f$N_contact_WT[D_data_f$Arena=='Large']),digits=2)`)
```{r Mean number of contacts in large arena size in females, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_f$N_contact_WT[D_data_f$Arena=='Large'],na.rm=T)
standard_error(D_data_f$N_contact_WT[D_data_f$Arena=='Large'])
```

Mean number of contacts in small arena size (SE) = `r round(mean(D_data_f$N_contact_WT[D_data_f$Arena=='Small'],na.rm=T),digits=2)` (`r round(standard_error(D_data_f$N_contact_WT[D_data_f$Arena=='Small']),digits=2)`)
```{r Mean number of contacts in small arena size in females, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_f$N_contact_WT[D_data_f$Arena=='Small'],na.rm=T)
standard_error(D_data_f$N_contact_WT[D_data_f$Arena=='Small'])
```

GLM for the effect of treatment on the number of contacts with potential partners:
```{r Model density effect on contact rates in females, warning=FALSE, message=FALSE}
mod2=glm((as.numeric(N_contact_WT))~Gr_size*Arena,data=D_data_f,family = quasipoisson) # GLM for treatment effect on contact rates of females
summary(mod2)
Anova(mod2,type=2) # Compute p-values via type 2 ANOVA
```
FDR corrected p-values:
```{r FDR corrected p-values in females, warning=FALSE, message=FALSE}
tab2=as.data.frame(round(p.adjust(c(2.432e-09, 1.084e-06,0.1754), method = 'fdr'),digits=3),row.names=cbind('Group size','Arena size', 'Interaction'))
colnames(tab2)<-cbind('P-value')
tab2
```

## Plot contact rates (Figure S1)

Here we plot the contact rates with potential partners per treatment and sex.
```{r Figure S1, warning=FALSE, message=FALSE, fig.align="left",fig.width = 11,fig.height=6, results='hide', fig.fullwidth=TRUE,fig.cap='Figure S1: Total number of contacts with potential mating partners for males and females under low and high density manipulation via group (left) and arena size (right). Bars indicate means and 95% CI.'}
## Plot contact rates (Figure S1) ####
# Create factor for treatment categories
D_data$TreatCgroup <- factor(paste(D_data$Sex,D_data$Gr_size,  sep=" "), levels = c("F SG", "F LG", "M SG",'M LG'))

p1=ggplot(D_data, aes(x=Sex, y=as.numeric(N_contact_WT),fill=TreatCgroup, col=TreatCgroup,alpha=TreatCgroup)) +
   geom_point(position=position_jitterdodge(jitter.width=0.5,jitter.height = 0,dodge.width=1.2),shape=19, size = 2)+
  stat_summary(fun.min =lower_CI ,
               fun.max = upper_CI ,fun = mean,
               position=position_dodge2(0.3),col=c("#b2182b","#b2182b","#2166AC","#2166AC"),alpha=c(0.5,0.75,0.5,0.75),show.legend = F, linewidth = 1.15)+
  stat_summary(fun = mean,
               position=position_dodge2(0.3), size = 1,col=c("white","white","white","white"),alpha=c(1,1,1,1),show.legend = F, stroke = 0,linewidth = 1.2)+
  stat_summary(fun = mean,
               position=position_dodge2(0.3), size = 1,col=c("#b2182b","#b2182b","#2166AC","#2166AC"),alpha=c(0.5,0.75,0.5,0.75),show.legend = F, stroke = 0,linewidth = 1.2)+
  scale_color_manual(values=c(colpal2[1],colpal2[1],colpal2[2],colpal2[2]),name = "Treatment", labels = c('Small group','Large group','Small group','Large group'))+
  scale_fill_manual(values=c(colpal2[1],colpal2[1],colpal2[2],colpal2[2]),name = "Treatment", labels = c('Small group','Large group','Small group','Large group'))+
  scale_alpha_manual(values=c(0.5,0.75,0.5,0.75),name = "Treatment", labels = c('Small group','Large group','Small group','Large group'))+
  xlab('Sex')+ylab("Contacts with mating partners")+ggtitle('')+ theme(plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c('Female','Male'),drop=FALSE)+ylim(0,400)+labs(tag = "A")+
  annotate("text",label='n =',x=0.55,y=400,size=4)+
  annotate("text",label='54',x=0.78,y=400,size=4)+
  annotate("text",label='45',x=1.23,y=400,size=4)+
  annotate("text",label='46',x=1.78,y=400,size=4)+
  annotate("text",label='58',x=2.23,y=400,size=4)+
  guides(colour = guide_legend(override.aes = list(size=4)))+
  fig_theme+theme( legend.position = c(1.2, 0.8))

# Create factor for treatment categories
D_data$TreatCarena <- factor(paste(D_data$Sex,D_data$Arena,  sep=" "), levels = c("F Large", "F Small", "M Large",'M Small'))

p2=ggplot(D_data, aes(x=Sex, y=as.numeric(N_contact_WT),fill=TreatCarena, col=TreatCarena,alpha=TreatCarena)) +
  geom_point(position=position_jitterdodge(jitter.width=0.5,jitter.height = 0,dodge.width=1.2),shape=19, size = 2)+
  stat_summary(fun.min =lower_CI ,
               fun.max = upper_CI ,fun = mean,
               position=position_dodge2(0.3),col=c("#b2182b","#b2182b","#2166AC","#2166AC"),alpha=c(0.5,0.75,0.5,0.75),show.legend = F, linewidth = 1.15)+
  stat_summary(fun = mean,
               position=position_dodge2(0.3), size = 1,col=c("white","white","white","white"),alpha=c(1,1,1,1),show.legend = F, stroke = 0,linewidth = 1.2)+
  stat_summary(fun = mean,
               position=position_dodge2(0.3), size = 1,col=c("#b2182b","#b2182b","#2166AC","#2166AC"),alpha=c(0.5,0.75,0.5,0.75),show.legend = F, stroke = 0,linewidth = 1.2)+
  scale_color_manual(values=c(colpal2[1],colpal2[1],colpal2[2],colpal2[2]),name = "Treatment", labels = c('Small arena','Large arena','Small arena','Large arena'))+
  scale_fill_manual(values=c(colpal2[1],colpal2[1],colpal2[2],colpal2[2]),name = "Treatment", labels = c('Small arena','Large arena','Small arena','Large arena'))+
  scale_alpha_manual(values=c(0.5,0.75,0.5,0.75),name = "Treatment", labels = c('Small arena','Large arena','Small arena','Large arena'))+
  xlab('Sex')+ylab("")+ggtitle('')+ theme(plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c('Female','Male'),drop=FALSE)+ylim(0,400)+labs(tag = "B")+
  annotate("text",label='n =',x=0.55,y=400,size=4)+
  annotate("text",label='51',x=0.78,y=400,size=4)+
  annotate("text",label='48',x=1.23,y=400,size=4)+
  annotate("text",label='55',x=1.78,y=400,size=4)+
  annotate("text",label='49',x=2.23,y=400,size=4)+
  guides(colour = guide_legend(override.aes = list(size=4)))+
  fig_theme+theme( legend.position = c(1.2, 0.8))

# Arrange figures
Figure_S1<-grid.arrange(grobs = list(p1+theme(plot.margin = unit(c(0.2,4,0,0.3), "cm")),p2+theme(plot.margin = unit(c(0.2,4,0,0.3), "cm"))), nrow = 1,ncol=2, widths=c(2.3, 2.3))
Figure_S1<-plot_grid(Figure_S1, ncol=1, rel_heights=c(0.1, 1))
```

# Bootstrapping the variance in contact rates

Next, we computed the coefficient of variation in contact rates for both sexes and all treatments.
```{r Bootstrapping the variance in contact rates, warning=FALSE, message=FALSE, results='hide'}
## Bootstrapping the variance in contact rates ####
# Male
# Large group size

D_data_Large_pop_M_Contact_n <-as.vector(D_data_Large_pop$N_contact_WT[D_data_Large_pop$Sex=='M'])
c <- function(d, i){
  d2 <- d[i]
  return(sd(d2, na.rm=TRUE)/mean(d2, na.rm=TRUE))
}
Large_pop_M_Contact_bootvar <- boot(D_data_Large_pop_M_Contact_n, c, R=10000)

# Small group size
D_data_Small_pop_M_Contact_n <-as.vector(D_data_Small_pop$N_contact_WT[D_data_Large_pop$Sex=='M'])

Small_pop_M_Contact_bootvar <- boot(D_data_Small_pop_M_Contact_n, c, R=10000)

# Large arena
D_data_Large_arena_M_Contact_n <-as.vector(D_data_Large_arena$N_contact_WT[D_data_Large_pop$Sex=='M'])

Large_arena_M_Contact_bootvar <- boot(D_data_Large_arena_M_Contact_n, c, R=10000)

# Small arena  
D_data_Small_arena_M_Contact_n <-as.vector(D_data_Small_arena$N_contact_WT[D_data_Large_pop$Sex=='M'])

Small_arena_M_Contact_bootvar <- boot(D_data_Small_arena_M_Contact_n, c, R=10000)

# Female
# Large group size
D_data_Large_pop_F_Contact_n <-as.vector(D_data_Large_pop$N_contact_WT[D_data_Large_pop$Sex=='F'])

Large_pop_F_Contact_bootvar <- boot(D_data_Large_pop_F_Contact_n, c, R=10000)

# Small group size
D_data_Small_pop_F_Contact_n <-as.vector(D_data_Small_pop$N_contact_WT[D_data_Large_pop$Sex=='F'])

Small_pop_F_Contact_bootvar <- boot(D_data_Small_pop_F_Contact_n, c, R=10000)

# Large arena
D_data_Large_arena_F_Contact_n <-as.vector(D_data_Large_arena$N_contact_WT[D_data_Large_pop$Sex=='F'])

Large_arena_F_Contact_bootvar <- boot(D_data_Large_arena_F_Contact_n, c, R=10000)

# Small arena  
D_data_Small_arena_F_Contact_n <-as.vector(D_data_Small_arena$N_contact_WT[D_data_Large_pop$Sex=='F'])

Small_arena_F_Contact_bootvar <- boot(D_data_Small_arena_F_Contact_n, c, R=10000)

# Extract data and write results table
PhenVarBoot_Table_Male_Small_pop_Contact <- as.data.frame(cbind("Male", "Small population size", "Contacts with pot. partners", as.numeric(mean(Small_pop_M_Contact_bootvar$t)), quantile(Small_pop_M_Contact_bootvar$t,.025, names = FALSE), quantile(Small_pop_M_Contact_bootvar$t,.975, names = FALSE)))
PhenVarBoot_Table_Male_Large_pop_Contact <- as.data.frame(cbind("Male", "Large population size", "Contacts with pot. partners", as.numeric(mean(Large_pop_M_Contact_bootvar$t)), quantile(Large_pop_M_Contact_bootvar$t,.025, names = FALSE), quantile(Large_pop_M_Contact_bootvar$t,.975, names = FALSE)))
PhenVarBoot_Table_Female_Small_pop_Contact <- as.data.frame(cbind("Female", "Small population size", "Contacts with pot. partners", as.numeric(mean(Small_pop_F_Contact_bootvar$t)), quantile(Small_pop_F_Contact_bootvar$t,.025, names = FALSE), quantile(Small_pop_F_Contact_bootvar$t,.975, names = FALSE)))
PhenVarBoot_Table_Female_Large_pop_Contact <- as.data.frame(cbind("Female", "Large population size", "Contacts with pot. partners", as.numeric(mean(Large_pop_F_Contact_bootvar$t)), quantile(Large_pop_F_Contact_bootvar$t,.025, names = FALSE), quantile(Large_pop_F_Contact_bootvar$t,.975, names = FALSE)))
PhenVarBoot_Table_Male_Small_arena_Contact <- as.data.frame(cbind("Male", "Small arena size", "Contacts with pot. partners", as.numeric(mean(Small_arena_M_Contact_bootvar$t)), quantile(Small_arena_M_Contact_bootvar$t,.025, names = FALSE), quantile(Small_arena_M_Contact_bootvar$t,.975, names = FALSE)))
PhenVarBoot_Table_Male_Large_arena_Contact <- as.data.frame(cbind("Male", "Large arena size", "Contacts with pot. partners", as.numeric(mean(Large_arena_M_Contact_bootvar$t)), quantile(Large_arena_M_Contact_bootvar$t,.025, names = FALSE), quantile(Large_arena_M_Contact_bootvar$t,.975, names = FALSE)))
PhenVarBoot_Table_Female_Small_arena_Contact <- as.data.frame(cbind("Female", "Small arena size", "Contacts with pot. partners", as.numeric(mean(Small_arena_F_Contact_bootvar$t)), quantile(Small_arena_F_Contact_bootvar$t,.025, names = FALSE), quantile(Small_arena_F_Contact_bootvar$t,.975, names = FALSE)))
PhenVarBoot_Table_Female_Large_arena_Contact <- as.data.frame(cbind("Female", "Large arena size", "Contacts with pot. partners", as.numeric(mean(Large_arena_F_Contact_bootvar$t)), quantile(Large_arena_F_Contact_bootvar$t,.025, names = FALSE), quantile(Large_arena_F_Contact_bootvar$t,.975, names = FALSE)))

Table_VarCont <- as.data.frame(as.matrix(rbind(PhenVarBoot_Table_Male_Small_pop_Contact,PhenVarBoot_Table_Male_Large_pop_Contact,
                                               PhenVarBoot_Table_Female_Small_pop_Contact,PhenVarBoot_Table_Female_Large_pop_Contact,
                                               PhenVarBoot_Table_Male_Small_arena_Contact,PhenVarBoot_Table_Male_Large_arena_Contact,
                                               PhenVarBoot_Table_Female_Small_arena_Contact,PhenVarBoot_Table_Female_Large_arena_Contact)))

is.table(Table_VarCont)
colnames(Table_VarCont)[1] <- "Sex"
colnames(Table_VarCont)[2] <- "Treatment"
colnames(Table_VarCont)[3] <- "Trait"
colnames(Table_VarCont)[4] <- "Variance"
colnames(Table_VarCont)[5] <- "l95_CI"
colnames(Table_VarCont)[6] <- "u95_CI"
Table_VarCont[,4]=round(as.numeric(Table_VarCont[,4]),digits=2)
Table_VarCont[,5]=round(as.numeric(Table_VarCont[,5]),digits=2)
Table_VarCont[,6]=round(as.numeric(Table_VarCont[,6]),digits=2)

rm(c) # Remove bootstrapping function
```

Table S2: Coefficients of variation (CV) in the total number of contacts with potential mating partners for treatments (group and arena) estimated for males and females with mean and 95%CI estimated via bootstrapping.
```{r , warning=FALSE, message=FALSE, layout="l-body-outset"}
kable(Table_VarCont)
```

## Permutation test for treatment comparison of contact rates

Here we test if the coefficient of variation differed between treatments (large vs small population size & small vs large arena size).
```{r Permutation test for treatment comparison of contact rates, warning=FALSE, message=FALSE, results='hide'}
## Permutation test for treatment comparison of contact rates ####
# Male
# Group size
Treat_diff_Male_pop_Contact=c(Large_pop_M_Contact_bootvar$t)-c(Small_pop_M_Contact_bootvar$t)

t_Treat_diff_Male_pop_Contact=mean(Treat_diff_Male_pop_Contact,na.rm=TRUE)
t_Treat_diff_Male_pop_Contact_lower=quantile(Treat_diff_Male_pop_Contact,.025,na.rm=TRUE)
t_Treat_diff_Male_pop_Contact_upper=quantile(Treat_diff_Male_pop_Contact,.975,na.rm=TRUE)

#Permutation test to calculate p value
comb_data=c(D_data_Large_pop$N_contact_WT[D_data_Large_pop$Sex=='M'],D_data_Small_pop$N_contact_WT[D_data_Small_pop$Sex=='M'])

diff.observed = sd(na.omit((D_data_Large_pop$N_contact_WT[D_data_Large_pop$Sex=='M'])))/mean(na.omit((D_data_Large_pop$N_contact_WT[D_data_Large_pop$Sex=='M'])))-sd(na.omit((D_data_Small_pop$N_contact_WT[D_data_Small_pop$Sex=='M'])))/mean(na.omit((D_data_Small_pop$N_contact_WT[D_data_Small_pop$Sex=='M'])))

number_of_permutations = 100000
diff.random = NULL
for (i in 1 : number_of_permutations) {
  
  # Sample from the combined data set
  a.random = sample (na.omit(comb_data), length(c(D_data_Large_pop$N_contact_WT[D_data_Large_pop$Sex=='M'])), TRUE)
  b.random = sample (na.omit(comb_data), length(c(D_data_Small_pop$N_contact_WT[D_data_Small_pop$Sex=='M'])), TRUE)
  
  # Null (permuated) difference
  diff.random[i] =  sd(na.omit(a.random))/mean(na.omit(a.random))-sd(na.omit(b.random))/mean(na.omit(b.random))
}

# P-value is the fraction of how many times the permuted difference is equal or more extreme than the observed difference

t_Treat_diff_Male_pop_Contact_p = sum(abs(diff.random) >= as.numeric(abs(diff.observed)))/   number_of_permutations

# Arena
Treat_diff_Male_arena_Contact=c(Small_arena_M_Contact_bootvar$t)-c(Large_arena_M_Contact_bootvar$t)

t_Treat_diff_Male_arena_Contact=mean(Treat_diff_Male_arena_Contact,na.rm=TRUE)
t_Treat_diff_Male_arena_Contact_lower=quantile(Treat_diff_Male_arena_Contact,.025,na.rm=TRUE)
t_Treat_diff_Male_arena_Contact_upper=quantile(Treat_diff_Male_arena_Contact,.975,na.rm=TRUE)

#Permutation test to calculate p value
comb_data=c(D_data_Large_arena$N_contact_WT[D_data_Large_arena$Sex=='M'],D_data_Small_arena$N_contact_WT[D_data_Small_arena$Sex=='M'])

diff.observed = sd(na.omit((D_data_Small_arena$N_contact_WT[D_data_Small_arena$Sex=='M'])))/mean(na.omit((D_data_Small_arena$N_contact_WT[D_data_Small_arena$Sex=='M'])))-sd(na.omit((D_data_Large_arena$N_contact_WT[D_data_Large_arena$Sex=='M'])))/mean(na.omit((D_data_Large_arena$N_contact_WT[D_data_Large_arena$Sex=='M']))) 

number_of_permutations = 100000
diff.random = NULL
for (i in 1 : number_of_permutations) {
  
  # Sample from the combined data set
  b.random = sample (na.omit(comb_data), length(c(D_data_Large_arena$N_contact_WT[D_data_Large_arena$Sex=='M'])), TRUE)
  a.random = sample (na.omit(comb_data), length(c(D_data_Small_arena$N_contact_WT[D_data_Small_arena$Sex=='M'])), TRUE)
  
  # Null (permuated) difference
  diff.random[i] =  sd(na.omit(a.random))/mean(na.omit(a.random))-sd(na.omit(b.random))/mean(na.omit(b.random))
}

t_Treat_diff_Male_arena_Contact_p = sum(abs(diff.random) >= as.numeric(abs(diff.observed)))/   number_of_permutations

# Female
# Group size
Treat_diff_Female_pop_Contact=c(Large_pop_F_Contact_bootvar$t)-c(Small_pop_F_Contact_bootvar$t)

t_Treat_diff_Female_pop_Contact=mean(Treat_diff_Female_pop_Contact,na.rm=TRUE)
t_Treat_diff_Female_pop_Contact_lower=quantile(Treat_diff_Female_pop_Contact,.025,na.rm=TRUE)
t_Treat_diff_Female_pop_Contact_upper=quantile(Treat_diff_Female_pop_Contact,.975,na.rm=TRUE)

#Permutation test to calculate p value
comb_data=c(D_data_Large_pop$N_contact_WT[D_data_Large_pop$Sex=='F'],D_data_Small_pop$N_contact_WT[D_data_Small_pop$Sex=='F'])

diff.observed = sd(na.omit((D_data_Large_pop$N_contact_WT[D_data_Large_pop$Sex=='F'])))/mean(na.omit((D_data_Large_pop$N_contact_WT[D_data_Large_pop$Sex=='F'])))- sd(na.omit((D_data_Small_pop$N_contact_WT[D_data_Small_pop$Sex=='F'])))/mean(na.omit((D_data_Small_pop$N_contact_WT[D_data_Small_pop$Sex=='F'])))

number_of_permutations = 100000
diff.random = NULL
for (i in 1 : number_of_permutations) {
  
  # Sample from the combined data set
  a.random = sample (na.omit(comb_data), length(c(D_data_Large_pop$N_contact_WT[D_data_Large_pop$Sex=='F'])), TRUE)
  b.random = sample (na.omit(comb_data), length(c(D_data_Small_pop$N_contact_WT[D_data_Small_pop$Sex=='F'])), TRUE)
  
  # Null (permuated) difference
  diff.random[i] =  sd(na.omit(a.random))/mean(na.omit(a.random))-sd(na.omit(b.random))/mean(na.omit(b.random))
}

t_Treat_diff_Female_pop_Contact_p = sum(abs(diff.random) >= as.numeric(abs(diff.observed)))/   number_of_permutations

# Arena
Treat_diff_Female_arena_Contact=c(Small_arena_F_Contact_bootvar$t)-c(Large_arena_F_Contact_bootvar$t)

t_Treat_diff_Female_arena_Contact=mean(Treat_diff_Female_arena_Contact,na.rm=TRUE)
t_Treat_diff_Female_arena_Contact_lower=quantile(Treat_diff_Female_arena_Contact,.025,na.rm=TRUE)
t_Treat_diff_Female_arena_Contact_upper=quantile(Treat_diff_Female_arena_Contact,.975,na.rm=TRUE)

#Permutation test to calculate p value
comb_data=c(D_data_Large_arena$N_contact_WT[D_data_Large_arena$Sex=='F'],D_data_Small_arena$N_contact_WT[D_data_Small_arena$Sex=='F'])

diff.observed = sd(na.omit((D_data_Small_arena$N_contact_WT[D_data_Small_arena$Sex=='F'])))/mean(na.omit((D_data_Small_arena$N_contact_WT[D_data_Small_arena$Sex=='F'])))-sd(na.omit((D_data_Large_arena$N_contact_WT[D_data_Large_arena$Sex=='F'])))/mean(na.omit((D_data_Large_arena$N_contact_WT[D_data_Large_arena$Sex=='F']))) 

number_of_permutations = 100000
diff.random = NULL
for (i in 1 : number_of_permutations) {
  
  # Sample from the combined data set
  b.random = sample (na.omit(comb_data), length(c(D_data_Large_arena$N_contact_WT[D_data_Large_arena$Sex=='F'])), TRUE)
  a.random = sample (na.omit(comb_data), length(c(D_data_Small_arena$N_contact_WT[D_data_Small_arena$Sex=='F'])), TRUE)
  
  # Null (permuated) difference
  diff.random[i] =  sd(na.omit(a.random))/mean(na.omit(a.random))-sd(na.omit(b.random))/mean(na.omit(b.random))
}

t_Treat_diff_Female_arena_Contact_p = sum(abs(diff.random) >= as.numeric(abs(diff.observed)))/   number_of_permutations

# Extract data and write data table
CompTreat_Table_Male_pop_Contact <- as.data.frame(cbind("Male", "Group size", "Contacts with pot. partners", t_Treat_diff_Male_pop_Contact, t_Treat_diff_Male_pop_Contact_lower, t_Treat_diff_Male_pop_Contact_upper, t_Treat_diff_Male_pop_Contact_p))
names(CompTreat_Table_Male_pop_Contact)=c('V1','V2','V3','V4','V5','V6','V7')
CompTreat_Table_Female_pop_Contact <- as.data.frame(cbind("Female", "Group size", "Contacts with pot. partners", t_Treat_diff_Female_pop_Contact, t_Treat_diff_Female_pop_Contact_lower, t_Treat_diff_Female_pop_Contact_upper, t_Treat_diff_Female_pop_Contact_p))
names(CompTreat_Table_Female_pop_Contact)=c('V1','V2','V3','V4','V5','V6','V7')
CompTreat_Table_Male_arena_Contact <- as.data.frame(cbind("Male", "Arena size", "Contacts with pot. partners", t_Treat_diff_Male_arena_Contact, t_Treat_diff_Male_arena_Contact_lower, t_Treat_diff_Male_arena_Contact_upper, t_Treat_diff_Male_arena_Contact_p))
names(CompTreat_Table_Male_arena_Contact)=c('V1','V2','V3','V4','V5','V6','V7')
CompTreat_Table_Female_arena_Contact <- as.data.frame(cbind("Female", "Arena size", "Contacts with pot. partners", t_Treat_diff_Female_arena_Contact, t_Treat_diff_Female_arena_Contact_lower, t_Treat_diff_Female_arena_Contact_upper, t_Treat_diff_Female_arena_Contact_p))
names(CompTreat_Table_Female_arena_Contact)=c('V1','V2','V3','V4','V5','V6','V7')

Table_varCont_TreatComp <- as.data.frame(as.matrix(rbind(CompTreat_Table_Male_pop_Contact,CompTreat_Table_Female_pop_Contact,
                                                         CompTreat_Table_Male_arena_Contact,CompTreat_Table_Female_arena_Contact)))

Table_varCont_TreatComp[,4]=as.numeric(Table_varCont_TreatComp[,4])
Table_varCont_TreatComp[,5]=as.numeric(Table_varCont_TreatComp[,5])
Table_varCont_TreatComp[,6]=as.numeric(Table_varCont_TreatComp[,6])
Table_varCont_TreatComp[,7]=as.numeric(Table_varCont_TreatComp[,7])

colnames(Table_varCont_TreatComp)[1] <- "Sex"
colnames(Table_varCont_TreatComp)[2] <- "Treatment"
colnames(Table_varCont_TreatComp)[3] <- "Trait"
colnames(Table_varCont_TreatComp)[4] <- "Variance"
colnames(Table_varCont_TreatComp)[5] <- "l95_CI"
colnames(Table_varCont_TreatComp)[6] <- "u95_CI"
colnames(Table_varCont_TreatComp)[7] <- "Adj. p-value"
Table_varCont_TreatComp[,7]=c(round(p.adjust(c(0.32852 ,0.61279   ), method = 'fdr'),digit=3),round(p.adjust(c(0.52590 ,0.24217    ), method = 'fdr'),digit=3))

Table_varCont_TreatComp[,4]=round(as.numeric(Table_varCont_TreatComp[,4]),digits=2)
Table_varCont_TreatComp[,5]=round(as.numeric(Table_varCont_TreatComp[,5]),digits=2)
Table_varCont_TreatComp[,6]=round(as.numeric(Table_varCont_TreatComp[,6]),digits=2)
Table_varCont_TreatComp[,7]=as.numeric(Table_varCont_TreatComp[,7])
rownames(Table_varCont_TreatComp) <- c()

round(p.adjust(c(0.32852 ,0.61279   ), method = 'fdr'),digit=3) # Calculate FDR adjusted p-values for males
round(p.adjust(c(0.52590 ,0.24217    ), method = 'fdr'),digit=3) # Calculate FDR adjusted p-values for females
```

Table S3: Influence of density treatment (group and arena size) on coefficients of variation (CV) in the total number of contacts with potential mating partners for treatments (group size and arena) estimated for males and females with mean and 95%CI estimated via bootstrapping. Negative effect sizes indicate larger values at lower density and positive effect sizes larger values at higher density. P-values corrected for multiple testing by FDR (Benjamini and Hochberg 1995).
```{r , warning=FALSE, message=FALSE, layout="l-body-outset"}
kable(Table_varCont_TreatComp)
```
