---
title: 'Population density affects sexual selection in an insect model'
author: "Lennart Winkler^1^, Ronja Eilhardt^1^ & Tim Janicke^1,2^ <br></br>  ^1^Applied Zoology, Technical University Dresden <br> ^2^Centre d’Écologie Fonctionnelle et Évolutive, UMR 5175, CNRS, Université de Montpellier</br>"
subtitle: 'Part 1: Analyses on the effect of the treatment on contact rates'
site: workflowr::wflow_site
output:
  workflowr::wflow_html
---

Supplementary material reporting R code for the manuscript 'Population density affects sexual selection in an insect model'.

# Part 1: Analyses on the effect of the treatment on contact rates

First, we tested for an effect of group and arena size on the number of contacts with potential mating partners.

# Load and prepare data

Before we started the analyses, we loaded all necessary packages and data.
```{r Load, message=FALSE, warning=FALSE, results='hide'}
rm(list = ls()) # Clear work environment

# Load R-packages ####
list_of_packages=cbind('ggeffects','ggplot2','gridExtra','lme4','lmerTest','readr','dplyr','EnvStats','cowplot','gridGraphics','car','RColorBrewer','boot','data.table','base','ICC','knitr')
lapply(list_of_packages, require, character.only = TRUE) 

# Load data set ####
D_data=read_delim("./data/Data_Winkler_et_al_2023_Denstiy.csv",";", escape_double = FALSE, trim_ws = TRUE)

# Set factors and levels for factors
D_data$Week=as.factor(D_data$Week)
D_data$Sex=as.factor(D_data$Sex)
D_data$Gr_size=as.factor(D_data$Gr_size)
D_data$Gr_size <- factor(D_data$Gr_size, levels=c("SG","LG"))
D_data$Arena=as.factor(D_data$Arena)

## Subset data set ####
### Data according to denstiy ####
D_data_0.26=D_data[D_data$Treatment=='D = 0.26',]
D_data_0.52=D_data[D_data$Treatment=='D = 0.52',]
D_data_0.67=D_data[D_data$Treatment=='D = 0.67',]
D_data_1.33=D_data[D_data$Treatment=='D = 1.33',]

### Subset data by sex ####
D_data_m=D_data[D_data$Sex=='M',]
D_data_f=D_data[D_data$Sex=='F',]

### Calculate data relativized within treatment and sex ####
# Small group + large Area
D_data_0.26=D_data[D_data$Treatment=='D = 0.26',]

D_data_0.26$rel_m_RS=NA
D_data_0.26$rel_m_prop_RS=NA
D_data_0.26$rel_m_cMS=NA
D_data_0.26$rel_m_InSuc=NA
D_data_0.26$rel_m_feSuc=NA
D_data_0.26$rel_m_pFec=NA
D_data_0.26$rel_m_PS=NA
D_data_0.26$rel_m_pFec_compl=NA

D_data_0.26$rel_f_RS=NA
D_data_0.26$rel_f_prop_RS=NA
D_data_0.26$rel_f_cMS=NA
D_data_0.26$rel_f_fec_pMate=NA

D_data_0.26$rel_m_RS=D_data_0.26$m_RS/mean(D_data_0.26$m_RS,na.rm=T)
D_data_0.26$rel_m_prop_RS=D_data_0.26$m_prop_RS/mean(D_data_0.26$m_prop_RS,na.rm=T)
D_data_0.26$rel_m_cMS=D_data_0.26$m_cMS/mean(D_data_0.26$m_cMS,na.rm=T)
D_data_0.26$rel_m_InSuc=D_data_0.26$m_InSuc/mean(D_data_0.26$m_InSuc,na.rm=T)
D_data_0.26$rel_m_feSuc=D_data_0.26$m_feSuc/mean(D_data_0.26$m_feSuc,na.rm=T)
D_data_0.26$rel_m_pFec=D_data_0.26$m_pFec/mean(D_data_0.26$m_pFec,na.rm=T)
D_data_0.26$rel_m_PS=D_data_0.26$m_PS/mean(D_data_0.26$m_PS,na.rm=T)
D_data_0.26$rel_m_pFec_compl=D_data_0.26$m_pFec_compl/mean(D_data_0.26$m_pFec_compl,na.rm=T)

D_data_0.26$rel_f_RS=D_data_0.26$f_RS/mean(D_data_0.26$f_RS,na.rm=T)
D_data_0.26$rel_f_prop_RS=D_data_0.26$f_prop_RS/mean(D_data_0.26$f_prop_RS,na.rm=T)
D_data_0.26$rel_f_cMS=D_data_0.26$f_cMS/mean(D_data_0.26$f_cMS,na.rm=T)
D_data_0.26$rel_f_fec_pMate=D_data_0.26$f_fec_pMate/mean(D_data_0.26$f_fec_pMate,na.rm=T)

# Large group + large Area
D_data_0.52=D_data[D_data$Treatment=='D = 0.52',]
#Relativize data

D_data_0.52$rel_m_RS=NA
D_data_0.52$rel_m_prop_RS=NA
D_data_0.52$rel_m_cMS=NA
D_data_0.52$rel_m_InSuc=NA
D_data_0.52$rel_m_feSuc=NA
D_data_0.52$rel_m_pFec=NA
D_data_0.52$rel_m_PS=NA
D_data_0.52$rel_m_pFec_compl=NA

D_data_0.52$rel_f_RS=NA
D_data_0.52$rel_f_prop_RS=NA
D_data_0.52$rel_f_cMS=NA
D_data_0.52$rel_f_fec_pMate=NA

D_data_0.52$rel_m_RS=D_data_0.52$m_RS/mean(D_data_0.52$m_RS,na.rm=T)
D_data_0.52$rel_m_prop_RS=D_data_0.52$m_prop_RS/mean(D_data_0.52$m_prop_RS,na.rm=T)
D_data_0.52$rel_m_cMS=D_data_0.52$m_cMS/mean(D_data_0.52$m_cMS,na.rm=T)
D_data_0.52$rel_m_InSuc=D_data_0.52$m_InSuc/mean(D_data_0.52$m_InSuc,na.rm=T)
D_data_0.52$rel_m_feSuc=D_data_0.52$m_feSuc/mean(D_data_0.52$m_feSuc,na.rm=T)
D_data_0.52$rel_m_pFec=D_data_0.52$m_pFec/mean(D_data_0.52$m_pFec,na.rm=T)
D_data_0.52$rel_m_PS=D_data_0.52$m_PS/mean(D_data_0.52$m_PS,na.rm=T)
D_data_0.52$rel_m_pFec_compl=D_data_0.52$m_pFec_compl/mean(D_data_0.52$m_pFec_compl,na.rm=T)

D_data_0.52$rel_f_RS=D_data_0.52$f_RS/mean(D_data_0.52$f_RS,na.rm=T)
D_data_0.52$rel_f_prop_RS=D_data_0.52$f_prop_RS/mean(D_data_0.52$f_prop_RS,na.rm=T)
D_data_0.52$rel_f_cMS=D_data_0.52$f_cMS/mean(D_data_0.52$f_cMS,na.rm=T)
D_data_0.52$rel_f_fec_pMate=D_data_0.52$f_fec_pMate/mean(D_data_0.52$f_fec_pMate,na.rm=T)

# Small group + small Area
D_data_0.67=D_data[D_data$Treatment=='D = 0.67',]
#Relativize data
D_data_0.67$rel_m_RS=NA
D_data_0.67$rel_m_prop_RS=NA
D_data_0.67$rel_m_cMS=NA
D_data_0.67$rel_m_InSuc=NA
D_data_0.67$rel_m_feSuc=NA
D_data_0.67$rel_m_pFec=NA
D_data_0.67$rel_m_PS=NA
D_data_0.67$rel_m_pFec_compl=NA

D_data_0.67$rel_f_RS=NA
D_data_0.67$rel_f_prop_RS=NA
D_data_0.67$rel_f_cMS=NA
D_data_0.67$rel_f_fec_pMate=NA

D_data_0.67$rel_m_RS=D_data_0.67$m_RS/mean(D_data_0.67$m_RS,na.rm=T)
D_data_0.67$rel_m_prop_RS=D_data_0.67$m_prop_RS/mean(D_data_0.67$m_prop_RS,na.rm=T)
D_data_0.67$rel_m_cMS=D_data_0.67$m_cMS/mean(D_data_0.67$m_cMS,na.rm=T)
D_data_0.67$rel_m_InSuc=D_data_0.67$m_InSuc/mean(D_data_0.67$m_InSuc,na.rm=T)
D_data_0.67$rel_m_feSuc=D_data_0.67$m_feSuc/mean(D_data_0.67$m_feSuc,na.rm=T)
D_data_0.67$rel_m_pFec=D_data_0.67$m_pFec/mean(D_data_0.67$m_pFec,na.rm=T)
D_data_0.67$rel_m_PS=D_data_0.67$m_PS/mean(D_data_0.67$m_PS,na.rm=T)
D_data_0.67$rel_m_pFec_compl=D_data_0.67$m_pFec_compl/mean(D_data_0.67$m_pFec_compl,na.rm=T)

D_data_0.67$rel_f_RS=D_data_0.67$f_RS/mean(D_data_0.67$f_RS,na.rm=T)
D_data_0.67$rel_f_prop_RS=D_data_0.67$f_prop_RS/mean(D_data_0.67$f_prop_RS,na.rm=T)
D_data_0.67$rel_f_cMS=D_data_0.67$f_cMS/mean(D_data_0.67$f_cMS,na.rm=T)
D_data_0.67$rel_f_fec_pMate=D_data_0.67$f_fec_pMate/mean(D_data_0.67$f_fec_pMate,na.rm=T)

# Large group + small Area
D_data_1.33=D_data[D_data$Treatment=='D = 1.33',]
#Relativize data

D_data_1.33$rel_m_RS=NA
D_data_1.33$rel_m_prop_RS=NA
D_data_1.33$rel_m_cMS=NA
D_data_1.33$rel_m_InSuc=NA
D_data_1.33$rel_m_feSuc=NA
D_data_1.33$rel_m_pFec=NA
D_data_1.33$rel_m_PS=NA
D_data_1.33$rel_m_pFec_compl=NA

D_data_1.33$rel_f_RS=NA
D_data_1.33$rel_f_prop_RS=NA
D_data_1.33$rel_f_cMS=NA
D_data_1.33$rel_f_fec_pMate=NA

D_data_1.33$rel_m_RS=D_data_1.33$m_RS/mean(D_data_1.33$m_RS,na.rm=T)
D_data_1.33$rel_m_prop_RS=D_data_1.33$m_prop_RS/mean(D_data_1.33$m_prop_RS,na.rm=T)
D_data_1.33$rel_m_cMS=D_data_1.33$m_cMS/mean(D_data_1.33$m_cMS,na.rm=T)
D_data_1.33$rel_m_InSuc=D_data_1.33$m_InSuc/mean(D_data_1.33$m_InSuc,na.rm=T)
D_data_1.33$rel_m_feSuc=D_data_1.33$m_feSuc/mean(D_data_1.33$m_feSuc,na.rm=T)
D_data_1.33$rel_m_pFec=D_data_1.33$m_pFec/mean(D_data_1.33$m_pFec,na.rm=T)
D_data_1.33$rel_m_PS=D_data_1.33$m_PS/mean(D_data_1.33$m_PS,na.rm=T)
D_data_1.33$rel_m_pFec_compl=D_data_1.33$m_pFec_compl/mean(D_data_1.33$m_pFec_compl,na.rm=T)

D_data_1.33$rel_f_RS=D_data_1.33$f_RS/mean(D_data_1.33$f_RS,na.rm=T)
D_data_1.33$rel_f_prop_RS=D_data_1.33$f_prop_RS/mean(D_data_1.33$f_prop_RS,na.rm=T)
D_data_1.33$rel_f_cMS=D_data_1.33$f_cMS/mean(D_data_1.33$f_cMS,na.rm=T)
D_data_1.33$rel_f_fec_pMate=D_data_1.33$f_fec_pMate/mean(D_data_1.33$f_fec_pMate,na.rm=T)

### Reduce treatments to arena and population size ####
# Arena size
D_data_Large_arena=rbind(D_data_0.26,D_data_0.52)
D_data_Small_arena=rbind(D_data_0.67,D_data_1.33)

# Population size
D_data_Small_pop=rbind(D_data_0.26,D_data_0.67)
D_data_Large_pop=rbind(D_data_0.52,D_data_1.33)

## Set figure schemes ####
# Set color-sets for figures
colpal=brewer.pal(4, 'Dark2')
colpal2=c("#b2182b","#2166AC")
colpal3=brewer.pal(4, 'Paired')

# Set theme for ggplot2 figures
fig_theme=theme(panel.border = element_blank(),
                plot.margin = margin(0,2.2,0,0.2,"cm"),
                plot.title = element_text(hjust = 0.5),
                panel.background = element_blank(),
                legend.key=element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(), 
                legend.position = c(1.25, 0.8),
                plot.tag.position=c(0.01,0.98),
                legend.title = element_blank(),
                legend.text = element_text(colour="black", size=10),
                axis.line.x = element_line(colour = "black", size = 1),
                axis.line.y = element_line(colour = "black", size = 1),
                axis.text.x = element_text(face="plain", color="black", size=16, angle=0),
                axis.text.y = element_text(face="plain", color="black", size=16, angle=0),
                axis.title.x = element_text(size=16,face="plain", margin = margin(r=0,10,0,0)),
                axis.title.y = element_text(size=16,face="plain", margin = margin(r=10,0,0,0)),
                axis.ticks = element_line(size = 1),
                axis.ticks.length = unit(.3, "cm"))

## Create customized functions for analysis ####
# Create function to calculate standard error and upper/lower standard deviation
standard_error <- function(x) sd(x,na.rm=T) / sqrt(length(na.exclude(x)))
upper_CI <- function(x) mean(x,na.rm=T)+((standard_error(x))*qnorm(0.975))
lower_CI <- function(x) mean(x,na.rm=T)-((standard_error(x))*qnorm(0.975))

upper_SD <- function(x) mean(x,na.rm=T)+(sd(x)/2)
lower_SD <- function(x) mean(x,na.rm=T)-(sd(x)/2)
```

# Effect of density on contact rates of males

First, we calculated means and SE for all treatments:</br></br>
Mean number of contacts in small groups (SE) = `r round(mean(D_data_m$N_contact_WT[D_data_m$Gr_size=='SG'],na.rm=T),digits=2)` (`r round(standard_error(D_data_m$N_contact_WT[D_data_m$Gr_size=='SG']),digits=2)`)
```{r Mean number of contacts in small groups, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_m$N_contact_WT[D_data_m$Gr_size=='SG'],na.rm=T)
standard_error(D_data_m$N_contact_WT[D_data_m$Gr_size=='SG'])
```

Mean number of contacts in large groups (SE) = `r round(mean(D_data_m$N_contact_WT[D_data_m$Gr_size=='LG'],na.rm=T),digits=2)` (`r round(standard_error(D_data_m$N_contact_WT[D_data_m$Gr_size=='LG']),digits=2)`)
```{r Mean number of contacts in large groups, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_m$N_contact_WT[D_data_m$Gr_size=='LG'],na.rm=T)
standard_error(D_data_m$N_contact_WT[D_data_m$Gr_size=='LG'])
```

Mean number of contacts in large arena size (SE) = `r round(mean(D_data_m$N_contact_WT[D_data_m$Arena=='Large'],na.rm=T),digits=2)` (`r round(standard_error(D_data_m$N_contact_WT[D_data_m$Arena=='Large']),digits=2)`)
```{r Mean number of contacts in large arena size, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_m$N_contact_WT[D_data_m$Arena=='Large'],na.rm=T)
standard_error(D_data_m$N_contact_WT[D_data_m$Arena=='Large'])
```

Mean number of contacts in small arena size (SE) = `r round(mean(D_data_m$N_contact_WT[D_data_m$Arena=='Small'],na.rm=T),digits=2)` (`r round(standard_error(D_data_m$N_contact_WT[D_data_m$Arena=='Small']),digits=2)`)
```{r Mean number of contacts in small arena size, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_m$N_contact_WT[D_data_m$Arena=='Small'],na.rm=T)
standard_error(D_data_m$N_contact_WT[D_data_m$Arena=='Small'])
```

GLM for the effect of treatment on the number of contacts with potential partners:
```{r Model density effect on contact rates in males, warning=FALSE, message=FALSE}
mod1=glm((as.numeric(N_contact_WT))~Gr_size*Arena,data=D_data_m,family = quasipoisson) # GLM for treatment effect on contact rates of males
summary(mod1)
Anova(mod1,type=2) # Compute p-values via type 2 ANOVA
```
FDR corrected p-values:
```{r FDR corrected p-values, warning=FALSE, message=FALSE}
tab1=as.data.frame(round(p.adjust(c(0.0021530,0.0004615,0.2541364), method = 'fdr'),digits=3),row.names=cbind('Group size','Arena size', 'Interaction'))
colnames(tab1)<-cbind('P-value')
tab1
```

## Effect of density on contact rates of females

We calculated means and SE for all treatments:</br></br>
Mean number of contacts in small groups (SE) = `r round(mean(D_data_f$N_contact_WT[D_data_f$Gr_size=='SG'],na.rm=T),digits=2)` (`r round(standard_error(D_data_f$N_contact_WT[D_data_f$Gr_size=='SG']),digits=2)`)
```{r Mean number of contacts in small groups in females, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_f$N_contact_WT[D_data_f$Gr_size=='SG'],na.rm=T)
standard_error(D_data_f$N_contact_WT[D_data_f$Gr_size=='SG'])
```

Mean number of contacts in large groups (SE) = `r round(mean(D_data_f$N_contact_WT[D_data_f$Gr_size=='LG'],na.rm=T),digits=2)` (`r round(standard_error(D_data_f$N_contact_WT[D_data_f$Gr_size=='LG']),digits=2)`)
```{r Mean number of contacts in large groups in females, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_f$N_contact_WT[D_data_f$Gr_size=='LG'],na.rm=T)
standard_error(D_data_f$N_contact_WT[D_data_f$Gr_size=='LG'])
```

Mean number of contacts in large arena size (SE) = `r round(mean(D_data_f$N_contact_WT[D_data_f$Arena=='Large'],na.rm=T),digits=2)` (`r round(standard_error(D_data_f$N_contact_WT[D_data_f$Arena=='Large']),digits=2)`)
```{r Mean number of contacts in large arena size in females, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_f$N_contact_WT[D_data_f$Arena=='Large'],na.rm=T)
standard_error(D_data_f$N_contact_WT[D_data_f$Arena=='Large'])
```

Mean number of contacts in small arena size (SE) = `r round(mean(D_data_f$N_contact_WT[D_data_f$Arena=='Small'],na.rm=T),digits=2)` (`r round(standard_error(D_data_f$N_contact_WT[D_data_f$Arena=='Small']),digits=2)`)
```{r Mean number of contacts in small arena size in females, warning=FALSE, message=FALSE, results='hide'}
mean(D_data_f$N_contact_WT[D_data_f$Arena=='Small'],na.rm=T)
standard_error(D_data_f$N_contact_WT[D_data_f$Arena=='Small'])
```

GLM for the effect of treatment on the number of contacts with potential partners:
```{r Model density effect on contact rates in females, warning=FALSE, message=FALSE}
mod2=glm((as.numeric(N_contact_WT))~Gr_size*Arena,data=D_data_f,family = quasipoisson) # GLM for treatment effect on contact rates of females
summary(mod2)
Anova(mod2,type=2) # Compute p-values via type 2 ANOVA
```
FDR corrected p-values:
```{r FDR corrected p-values in females, warning=FALSE, message=FALSE}
tab2=as.data.frame(round(p.adjust(c(2.432e-09, 1.084e-06,0.1754), method = 'fdr'),digits=3),row.names=cbind('Group size','Arena size', 'Interaction'))
colnames(tab2)<-cbind('P-value')
tab2
```

## Plot contact rates (Figure S1)

Here we plot the contact rates with potential partners per treatment and sex.
```{r Figure S1, warning=FALSE, message=FALSE, fig.align="left",fig.width = 11,fig.height=6, results='hide', fig.fullwidth=TRUE,fig.cap='Figure S1: Total number of contacts with potential mating partners for males and females under low and high density manipulation via group (left) and arena size (right). Bars indicate means and 95% CI.'}
## Plot contact rates (Figure S1) ####
# Create factor for treatment categories
D_data$TreatCgroup <- factor(paste(D_data$Sex,D_data$Gr_size,  sep=" "), levels = c("F SG", "F LG", "M SG",'M LG'))

p1=ggplot(D_data, aes(x=Sex, y=as.numeric(N_contact_WT),fill=TreatCgroup, col=TreatCgroup,alpha=TreatCgroup)) +
   geom_point(position=position_jitterdodge(jitter.width=0.5,jitter.height = 0,dodge.width=1.2),shape=19, size = 2)+
  stat_summary(fun.min =lower_CI ,
               fun.max = upper_CI ,fun = mean,
               position=position_dodge2(0.3),col=c("#b2182b","#b2182b","#2166AC","#2166AC"),alpha=c(0.5,0.75,0.5,0.75),show.legend = F, linewidth = 1.15)+
  stat_summary(fun = mean,
               position=position_dodge2(0.3), size = 1,col=c("white","white","white","white"),alpha=c(1,1,1,1),show.legend = F, stroke = 0,linewidth = 1.2)+
  stat_summary(fun = mean,
               position=position_dodge2(0.3), size = 1,col=c("#b2182b","#b2182b","#2166AC","#2166AC"),alpha=c(0.5,0.75,0.5,0.75),show.legend = F, stroke = 0,linewidth = 1.2)+
  scale_color_manual(values=c(colpal2[1],colpal2[1],colpal2[2],colpal2[2]),name = "Treatment", labels = c('Small group','Large group','Small group','Large group'))+
  scale_fill_manual(values=c(colpal2[1],colpal2[1],colpal2[2],colpal2[2]),name = "Treatment", labels = c('Small group','Large group','Small group','Large group'))+
  scale_alpha_manual(values=c(0.5,0.75,0.5,0.75),name = "Treatment", labels = c('Small group','Large group','Small group','Large group'))+
  xlab('Sex')+ylab("Contacts with mating partners")+ggtitle('')+ theme(plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c('Female','Male'),drop=FALSE)+ylim(0,400)+labs(tag = "A")+
  annotate("text",label='n =',x=0.55,y=400,size=4)+
  annotate("text",label='54',x=0.78,y=400,size=4)+
  annotate("text",label='45',x=1.23,y=400,size=4)+
  annotate("text",label='46',x=1.78,y=400,size=4)+
  annotate("text",label='58',x=2.23,y=400,size=4)+
  guides(colour = guide_legend(override.aes = list(size=4)))+
  fig_theme+theme( legend.position = c(1.2, 0.8))

# Create factor for treatment categories
D_data$TreatCarena <- factor(paste(D_data$Sex,D_data$Arena,  sep=" "), levels = c("F Large", "F Small", "M Large",'M Small'))

p2=ggplot(D_data, aes(x=Sex, y=as.numeric(N_contact_WT),fill=TreatCarena, col=TreatCarena,alpha=TreatCarena)) +
  geom_point(position=position_jitterdodge(jitter.width=0.5,jitter.height = 0,dodge.width=1.2),shape=19, size = 2)+
  stat_summary(fun.min =lower_CI ,
               fun.max = upper_CI ,fun = mean,
               position=position_dodge2(0.3),col=c("#b2182b","#b2182b","#2166AC","#2166AC"),alpha=c(0.5,0.75,0.5,0.75),show.legend = F, linewidth = 1.15)+
  stat_summary(fun = mean,
               position=position_dodge2(0.3), size = 1,col=c("white","white","white","white"),alpha=c(1,1,1,1),show.legend = F, stroke = 0,linewidth = 1.2)+
  stat_summary(fun = mean,
               position=position_dodge2(0.3), size = 1,col=c("#b2182b","#b2182b","#2166AC","#2166AC"),alpha=c(0.5,0.75,0.5,0.75),show.legend = F, stroke = 0,linewidth = 1.2)+
  scale_color_manual(values=c(colpal2[1],colpal2[1],colpal2[2],colpal2[2]),name = "Treatment", labels = c('Small arena','Large arena','Small arena','Large arena'))+
  scale_fill_manual(values=c(colpal2[1],colpal2[1],colpal2[2],colpal2[2]),name = "Treatment", labels = c('Small arena','Large arena','Small arena','Large arena'))+
  scale_alpha_manual(values=c(0.5,0.75,0.5,0.75),name = "Treatment", labels = c('Small arena','Large arena','Small arena','Large arena'))+
  xlab('Sex')+ylab("")+ggtitle('')+ theme(plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c('Female','Male'),drop=FALSE)+ylim(0,400)+labs(tag = "B")+
  annotate("text",label='n =',x=0.55,y=400,size=4)+
  annotate("text",label='51',x=0.78,y=400,size=4)+
  annotate("text",label='48',x=1.23,y=400,size=4)+
  annotate("text",label='55',x=1.78,y=400,size=4)+
  annotate("text",label='49',x=2.23,y=400,size=4)+
  guides(colour = guide_legend(override.aes = list(size=4)))+
  fig_theme+theme( legend.position = c(1.2, 0.8))

# Arrange figures
Figure_S1<-grid.arrange(grobs = list(p1+theme(plot.margin = unit(c(0.2,4,0,0.3), "cm")),p2+theme(plot.margin = unit(c(0.2,4,0,0.3), "cm"))), nrow = 1,ncol=2, widths=c(2.3, 2.3))
Figure_S1<-plot_grid(Figure_S1, ncol=1, rel_heights=c(0.1, 1))
```
